---
author: "Keerthana Jagadeesh"
date: "24 June 2019"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Vendor Survey Analysis 

This document goes through the analysis steps for the vendor survey data.

The in-detail summaries of all the questions were done in stata, and further analysis is shown here. 
??
```{r, echo=FALSE}
## import all the packages needed
library(plyr)
remove.packages("ggplot2") # Unisntall ggplot
install.packages("ggplot2") # Install it again
library(ggplot2)
library(dplyr)
library(readxl)
source("http://pcwww.liv.ac.uk/~william/R/crosstab.r")

## import the master dataset
core_peri <- read_excel("C:/Users/kjagadeesh/Dropbox/hungry cities survey/data/med_master_v1/core_peri_master.xlsx")



```
## Core-peri by owner age and business tenure

1 - outside bmp
0 - inside bmp
```{r, echo=FALSE}
count(core_peri, 'outside_bmp')


## owner age
crosstab(core_peri, row.vars = "outside_bmp", col.vars = "age", type = "r", addmargins = FALSE, dec.places=0)
```
##Business years breakdown: 
1 - Less than 1 year
2 - 1 - 5 years
3 - 5 - 10 years
4 - 10 - 20 years
5 - Greater than 20
```{r, echo=FALSE}

## biz tenure
crosstab(core_peri, row.vars = "outside_bmp", col.vars = "biz_years", type = "r", addmargins = FALSE, dec.places=0)
 
```
## Land use - broad by owner age and business tenure
```{r, echo=FALSE}
count(core_peri, 'land_use')


## owner age
crosstab(core_peri, row.vars = "land_use", col.vars = "age", type = "r", addmargins = FALSE, dec.places=0)
```
##Business years breakdown: 
1 - Less than 1 year
2 - 1 - 5 years
3 - 5 - 10 years
4 - 10 - 20 years
5 - Greater than 20
```{r, echo=FALSE}

## biz tenure
crosstab(core_peri, row.vars = "land_use", col.vars = "biz_years", type = "r", addmargins = FALSE, dec.places=0)
```
## Detailed Land use - by owner age and business tenure
```{r, echo=FALSE}
count(core_peri, 'det_land_use')


## owner age
crosstab(core_peri, row.vars = "det_land_use", col.vars = "age", type = "r", addmargins = FALSE, dec.places=0)
```
##Business years breakdown: 
1 - Less than 1 year
2 - 1 - 5 years
3 - 5 - 10 years
4 - 10 - 20 years
5 - Greater than 20
```{r, echo=FALSE}

## biz tenure
crosstab(core_peri, row.vars = "det_land_use", col.vars = "biz_years", type = "r", addmargins = FALSE, dec.places=0)
```
## From place - by owner age and business tenure
1 - this city
2 - rural KAR
3 - rural in another state or in country
4 - another city in the country
5 - another city in KAR
```{r, echo=FALSE}
count(core_peri, 'from_place')


## owner age
crosstab(core_peri, row.vars = "from_place", col.vars = "age", type = "r", addmargins = FALSE, dec.places=0)
```
##Business years breakdown: 
1 - Less than 1 year
2 - 1 - 5 years
3 - 5 - 10 years
4 - 10 - 20 years
5 - Greater than 20
```{r, echo=FALSE}

## biz tenure
crosstab(core_peri, row.vars = "from_place", col.vars = "biz_years", type = "r", addmargins = FALSE, dec.places=0) 
```
## Migrant Recency - by owner age and business tenure
```{r, echo=FALSE}
count(core_peri, 'migrant_rec')


## owner age
crosstab(core_peri, row.vars = "migrant_rec", col.vars = "age", type = "r", addmargins = FALSE, dec.places=0)
```
##Business years breakdown: 
1 - Less than 1 year
2 - 1 - 5 years
3 - 5 - 10 years
4 - 10 - 20 years
5 - Greater than 20
```{r, echo=FALSE}

## biz tenure
crosstab(core_peri, row.vars = "migrant_rec", col.vars = "biz_years", type = "r", addmargins = FALSE, dec.places=0) 
```   
## Education - by owner age and business tenure
  //1	No formal education
  //2	Some primary school (Between Class I-VIII) (but not completed)
  //3	Primary school completed (Passed Class VIII)
  //4	Some high school (Between Class IX-XVII) (but not completed)
  //5	High school completed (Passed Class XII)
  //6	University/college (but not completed degree)
  //7	University/college completed
```{r, echo=FALSE}
count(core_peri, 'var_33')


## owner age
crosstab(core_peri, row.vars = "var_33", col.vars = "age", type = "r", addmargins = FALSE, dec.places=0)
```
##Business years breakdown: 
1 - Less than 1 year
2 - 1 - 5 years
3 - 5 - 10 years
4 - 10 - 20 years
5 - Greater than 20
```{r, echo=FALSE}

## biz tenure
crosstab(core_peri, row.vars = "var_33", col.vars = "biz_years", type = "r", addmargins = FALSE, dec.places=0) 
``` 
## Migrants (from_place) by detailed land use type 

1 - this city
2 - rural KAR
3 - rural in another state or in country
4 - another city in the country
5 - another city in KAR
```{r, echo=FALSE}

## from_place by detailed land use type 
crosstab(core_peri, row.vars = "det_land_use", col.vars = "from_place", type = "r", addmargins = FALSE,  dec.places=0)
```
## Migrants (from_place) by core-peri 

1 - this city
2 - rural KAR
3 - rural in another state or in country
4 - another city in the country
5 - another city in KAR
```{r, echo=FALSE}

## from_place by detailed land use type 
crosstab(core_peri, row.vars = "from_place", col.vars = "outside_bmp", type = "r", addmargins = FALSE, dec.places=0)
```
## Migrant recency by core-peri 
1 - "Less than 2 years"
2 - "More than 2 years and less than 5 years"
3 - "More than 5 years and less than 10 years"
4 - "More than 10 years and less than 15 years"
5 - "More than 15 years and less than 20 years"
6 - "More than 20 years and less than 25 years"
7 - "More than 25"
```{r, echo=FALSE}

## from_place by detailed land use type 
crosstab(core_peri, row.vars = "migrant_rec", col.vars = "outside_bmp", type = "r", addmargins = FALSE, dec.places= 0)
```
## Migrant recency by detailed land use 
1 - "Less than 2 years"
2 - "More than 2 years and less than 5 years"
3 - "More than 5 years and less than 10 years"
4 - "More than 10 years and less than 15 years"
5 - "More than 15 years and less than 20 years"
6 - "More than 20 years and less than 25 years"
7 - "More than 25"
```{r, echo=FALSE}

## from_place by detailed land use type 
crosstab(core_peri, row.vars = "migrant_rec", col.vars = "det_land_use", type = "r", addmargins = FALSE, dec.places= 0)
```
## Profits for all groups

## Profit by location code
```{r, echo= FALSE}

# group_by(core_peri, location_code) %>%
#   summarise(
#     ##count = n(var_122),
#     mean = mean(var_122, na.rm = TRUE),
#     sd = sd(var_122, na.rm = TRUE)
#   )

loca <- ggplot(core_peri, aes(location_code, var_122))

loca + geom_boxplot(outlier.colour = "red") + coord_flip()

##boxplot(var_122~location_code, data=core_peri, notch=TRUE,
  ##main="Profit by location code", xlab="location codes", ylim = c(0, 30000))
```
## Profit by core-peri
```{r, echo= FALSE}

# group_by(core_peri, outside_bmp) %>%
#   summarise(
#     count = n(),
#     mean = mean(var_122, na.rm = TRUE),
#     sd = sd(var_122, na.rm = TRUE)
#   )

core <- ggplot(core_peri, aes(outside_bmp, var_122))

core + geom_boxplot(outlier.colour = "red") + coord_flip()

##boxplot(var_122~outside_bmp, data=core_peri, notch=TRUE,
  ##main="Profit by core-peri", xlab="core-peri", ylim = c(0, 30000))

```
## Profit by detailed land use
```{r, echo= FALSE}

# group_by(core_peri, det_land_use) %>%
#   summarise(
#     count = n(),
#     mean = mean(var_122, na.rm = TRUE),
#     sd = sd(var_122, na.rm = TRUE)
#   )

d_land <- ggplot(core_peri, aes(det_land_use, var_122))

d_land + geom_boxplot(outlier.colour = "red") + coord_flip()

##boxplot(var_122~det_land_use, data=core_peri, notch=TRUE,
  ##main="Profit by det_land_use", xlab="det_land_use", ylim = c(0, 30000))

```
## Profit by land use
```{r, echo= FALSE}

# group_by(core_peri, land_use) %>%
#   summarise(
#     count = n(),
#     mean = mean(var_122, na.rm = TRUE),
#     sd = sd(var_122, na.rm = TRUE)
#   )

land <- ggplot(core_peri, aes(land_use, var_122))

land + geom_boxplot(outlier.colour = "red") + coord_flip()

##boxplot(var_122~det_land_use, data=core_peri, notch=TRUE,
  ##main="Profit by land_use", xlab="land_use", ylim = c(0, 30000))

```
## Profit by from place
```{r, echo= FALSE}

# group_by(core_peri, from_place) %>%
#   summarise(
#     count = n(),
#     mean = mean(var_122, na.rm = TRUE),
#     sd = sd(var_122, na.rm = TRUE)
#   )

fromplace <- ggplot(core_peri, aes(from_place, var_122))

fromplace + geom_boxplot(outlier.colour = "red") + coord_flip()


##boxplot(var_122~from_place, data=core_peri, notch=TRUE,
  ##main="Profit by from place", xlab="from_place", ylim = c(0, 30000))

```
## Profit by migrant recency
```{r, echo= FALSE}

# group_by(core_peri, migrant_rec) %>%
#   summarise(
#     count = n(),
#     mean = mean(var_122, na.rm = TRUE),
#     sd = sd(var_122, na.rm = TRUE)
#   )

migrant_rec_box <- ggplot(core_peri, aes(migrant_rec, var_122))

migrant_rec_box + geom_boxplot(outlier.colour = "red") + coord_flip()

##boxplot(var_122~migrant_rec, data=core_peri, notch=TRUE,
  ##main="Profit by migrant recency", xlab="migrant recency", ylim = c(0, 30000))

```
## Profit by education
```{r, echo= FALSE}

# group_by(core_peri, var_33) %>%
#   summarise(
#     count = n(),
#     mean = mean(var_122, na.rm = TRUE),
#     sd = sd(var_122, na.rm = TRUE)
#   )
var_33_box <- ggplot(core_peri, aes(var_33, var_122))

var_33_box + geom_boxplot(outlier.colour = "red") + coord_flip()


##boxplot(var_122~var_33, data=core_peri, notch=TRUE,
  ##main="Profit by education", xlab="education", ylim = c(0, 30000))

```
## Startup capitals for all groups

## Startup capital by location code
```{r, echo= FALSE}

# group_by(core_peri, location_code) %>%
#   summarise(
#     count = n(),
#     mean = mean(var_82, na.rm = TRUE),
#     sd = sd(var_82, na.rm = TRUE)
#   )

loca_s <- ggplot(core_peri, aes(location_code, var_82))

loca_s + geom_boxplot(outlier.colour = "red") + coord_flip()



##boxplot(var_82~location_code, data=core_peri, notch=TRUE,
  ##main="Startup capital by location code", xlab="location codes", ylim = c(0, 30000))
```
## Startup capital by core-peri
```{r, echo= FALSE}

# group_by(core_peri, outside_bmp) %>%
#   summarise(
#     count = n(),
#     mean = mean(var_82, na.rm = TRUE),
#     sd = sd(var_82, na.rm = TRUE)
#   )

core_s <- ggplot(core_peri, aes(outside_bmp, var_82))

core_s + geom_boxplot(outlier.colour = "red") + coord_flip()

##boxplot(var_82~outside_bmp, data=core_peri, notch=TRUE,
  ##main="Startup capital by core-peri", xlab="core-peri", ylim = c(0, 30000))

```
## Startup capital by detailed land use
```{r, echo= FALSE}

# group_by(core_peri, det_land_use) %>%
#   summarise(
#     count = n(),
#     mean = mean(var_82, na.rm = TRUE),
#     sd = sd(var_82, na.rm = TRUE)
#   )

d_land_s <- ggplot(core_peri, aes(det_land_use, var_82))

d_land_s + geom_boxplot(outlier.colour = "red") + coord_flip()

##boxplot(var_82~det_land_use, data=core_peri, notch=TRUE,
  ##main="Startup capital by det_land_use", xlab="det_land_use", ylim = c(0, 30000))

```
## Startup capital by land use
```{r, echo= FALSE}

# group_by(core_peri, land_use) %>%
#   summarise(
#     count = n(),
#     mean = mean(var_82, na.rm = TRUE),
#     sd = sd(var_82, na.rm = TRUE)
#   )

land_s <- ggplot(core_peri, aes(land_use, var_82))

land_s + geom_boxplot(outlier.colour = "red") + coord_flip()


##boxplot(var_82~det_land_use, data=core_peri, notch=TRUE,
  ##main="Startup capital by land_use", xlab="land_use", ylim = c(0, 30000))

```
## Startup capital by from place
```{r, echo= FALSE}

# group_by(core_peri, from_place) %>%
#   summarise(
#     count = n(),
#     mean = mean(var_82, na.rm = TRUE),
#     sd = sd(var_82, na.rm = TRUE)
#   )

from_place_s <- ggplot(core_peri, aes(from_place, var_82))

from_place_s + geom_boxplot(outlier.colour = "red") + coord_flip()


##boxplot(var_82~from_place, data=core_peri, notch=TRUE,
  ##main="Startup capital by from place", xlab="from_place", ylim = c(0, 30000))

```
## Startup capital by migrant recency
```{r, echo= FALSE}

# group_by(core_peri, migrant_rec) %>%
#   summarise(
#     count = n(),
#     mean = mean(var_82, na.rm = TRUE),
#     sd = sd(var_82, na.rm = TRUE)
#   )

migrant_rec_s <- ggplot(core_peri, aes(migrant_rec, var_82))

migrant_rec_s + geom_boxplot(outlier.colour = "red") + coord_flip()

##boxplot(var_82~migrant_rec, data=core_peri, notch=TRUE,
  ##main="Startup capital by migrant recency", xlab="migrant recency", ylim = c(0, 30000))

```
## Startup capital by education
```{r, echo= FALSE}

# group_by(core_peri, var_33) %>%
#   summarise(
#     count = n(),
#     mean = mean(var_82, na.rm = TRUE),
#     sd = sd(var_82, na.rm = TRUE)
#   )

education_s <- ggplot(core_peri, aes(var_33, var_82))

education_s + geom_boxplot(outlier.colour = "red") + coord_flip()


##boxplot(var_82~var_33, data=core_peri, notch=TRUE,
  ##main="Startup capital by education", xlab="education", ylim = c(0, 30000))

```
<!-- ## Mod-startup capitals for all groups -->

<!-- ## Mod-startup capital by location code -->
<!-- ```{r, echo= FALSE} -->

<!-- group_by(core_peri, location_code) %>% -->
<!--   summarise( -->
<!--     count = n(), -->
<!--     mean = mean(mod_startup, na.rm = TRUE), -->
<!--     sd = sd(mod_startup, na.rm = TRUE) -->
<!--   ) -->

<!-- boxplot(mod_startup~location_code, data=core_peri, notch=TRUE, -->
<!--   main="Mod-startup capital by location code", xlab="location codes", ylim = c(0, 30000)) -->
<!-- ``` -->
<!-- ## Mod-startup capital by core-peri -->
<!-- ```{r, echo= FALSE} -->

<!-- group_by(core_peri, outside_bmp) %>% -->
<!--   summarise( -->
<!--     count = n(), -->
<!--     mean = mean(mod_startup, na.rm = TRUE), -->
<!--     sd = sd(mod_startup, na.rm = TRUE) -->
<!--   ) -->

<!-- boxplot(mod_startup~outside_bmp, data=core_peri, notch=TRUE, -->
<!--   main="Mod-startup capital by core-peri", xlab="core-peri", ylim = c(0, 30000)) -->

<!-- ``` -->
<!-- ## Mod-startup capital by detailed land use -->
<!-- ```{r, echo= FALSE} -->

<!-- group_by(core_peri, det_land_use) %>% -->
<!--   summarise( -->
<!--     count = n(), -->
<!--     mean = mean(mod_startup, na.rm = TRUE), -->
<!--     sd = sd(mod_startup, na.rm = TRUE) -->
<!--   ) -->

<!-- boxplot(mod_startup~det_land_use, data=core_peri, notch=TRUE, -->
<!--   main="Mod-startup capital by det_land_use", xlab="det_land_use", ylim = c(0, 30000)) -->

<!-- ``` -->
<!-- ## Mod-startup capital by land use -->
<!-- ```{r, echo= FALSE} -->

<!-- group_by(core_peri, land_use) %>% -->
<!--   summarise( -->
<!--     count = n(), -->
<!--     mean = mean(mod_startup, na.rm = TRUE), -->
<!--     sd = sd(mod_startup, na.rm = TRUE) -->
<!--   ) -->

<!-- boxplot(mod_startup~det_land_use, data=core_peri, notch=TRUE, -->
<!--   main="Mod-startup capital by land_use", xlab="land_use", ylim = c(0, 30000)) -->

<!-- ``` -->
<!-- ## Mod-startup capital by from place -->
<!-- ```{r, echo= FALSE} -->

<!-- group_by(core_peri, from_place) %>% -->
<!--   summarise( -->
<!--     count = n(), -->
<!--     mean = mean(mod_startup, na.rm = TRUE), -->
<!--     sd = sd(mod_startup, na.rm = TRUE) -->
<!--   ) -->

<!-- boxplot(mod_startup~from_place, data=core_peri, notch=TRUE, -->
<!--   main="Mod-startup capital by from place", xlab="from_place", ylim = c(0, 30000)) -->

<!-- ``` -->
<!-- ## Mod-startup capital by migrant recency -->
<!-- ```{r, echo= FALSE} -->

<!-- group_by(core_peri, migrant_rec) %>% -->
<!--   summarise( -->
<!--     count = n(), -->
<!--     mean = mean(mod_startup, na.rm = TRUE), -->
<!--     sd = sd(mod_startup, na.rm = TRUE) -->
<!--   ) -->

<!-- boxplot(mod_startup~migrant_rec, data=core_peri, notch=TRUE, -->
<!--   main="Mod-startup capital by migrant recency", xlab="migrant recency", ylim = c(0, 30000)) -->

<!-- ``` -->
<!-- ## Mod-startup capital by education -->
<!-- ```{r, echo= FALSE} -->

<!-- group_by(core_peri, var_33) %>% -->
<!--   summarise( -->
<!--     count = n(), -->
<!--     mean = mean(mod_startup, na.rm = TRUE), -->
<!--     sd = sd(mod_startup, na.rm = TRUE) -->
<!--   ) -->

<!-- boxplot(mod_startup~var_33, data=core_peri, notch=TRUE, -->
<!--   main="Mod-startup capital by education", xlab="education", ylim = c(0, 30000)) -->

<!-- ``` -->
